---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# GanaderiaSostenible

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/datasketch/GanaderiaSostenible.svg?branch=master)](https://travis-ci.org/datasketch/GanaderiaSostenible)
<!-- badges: end -->

Make sure to read the methodology (included in the package)

This package comes with its own webpage. Check out the following package notes.

- [How to run the app](https://datasketch.github.io/GanaderiaSostenible/articles/how-to-run-the-app.html)
- [How to use the package to calculate carbon capture for a given region in Colombia](https://datasketch.github.io/GanaderiaSostenible/articles/how-to-run-the-app.html)
- And more...


## Installation

You can install the released version of GanaderiaSostenible from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("GanaderiaSostenible")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("datasketch/GanaderiaSostenible")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## library(GanaderiaSostenible)
## basic example code
## GanaderiaSostenible::runApp()
```




